Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2015-10-16 icde2016/testing.tex
Added text motivating using public

The training data and test data are taken from data sets published to a free, online data analysis website. The published data includes both the raw data and how it was used for analysis. The service limits data sets to a maximum of 100K rows stored in a columnar database with collated strings.

@@

Most database and spreadsheet systems already detect a limited set of date formats. For instance, typing the string \texttt{"12/31/1999"} into Microsoft Excel, is automatically interpreted as the date \texttt{1999-12-31}. The Microsoft Jet library used to read these text files detects a few date formats as well. Any column already converted by Excel or Jet was not included in this study.

@@

\subsubsection{Sampling}
The remaining samples were hashed and sorted on the hash value, with the top 32 values being retained as the column's sample. We can increase the sample size if needed, but for dates, it appears to be an adequate number. In any case, the median number of non-null rows per domain in our test data is 50, so increasing the sample size would have little benefit.

@@

\subsubsection{Natural Language Processing}
We implemented the grammar, training and parsing in Python 3.4.1 using the Natural Language Toolkit libraries~\cite{nltk} on a quad core Dell T7600 running Windows 7. The complexity of the CYK parsing algorithm is $O(n^{3}|G|)$, where $n$ is the length of the input and $|G|$ is the size of the grammar~\cite{Younger67}. The PCFG grammar uses a set of $22$ phrase-level non-terminals and $30$ terminals to classify the various constituents in the corpus. Because the CYK algorithm finds the maximum likelihood solution, there are no search errors (rather probability $p = 0$, and a modification in the grammar is required to improve accuracy.

>>>>

The training data and test data are taken from data sets published to a free, online data analysis website. This website contains data sets that users analyzed and were interested in sharing with other people through the web. It may not be representative of data in other settings such as corporate data warehouses, but each data set is one that a user was willing to invest some time in analyzing. The published data includes both the raw data and how it was used for analysis. The service limits data sets to a maximum of 100K rows stored in a columnar database with collated strings.

@@

Most database and spreadsheet systems already detect a limited set of date formats. For instance, typing the string \texttt{"12/31/1999"} into Microsoft Excel, is automatically interpreted as the date \texttt{1999-12-31}. The Microsoft Jet library \vidya{need a reference here} used to read these text files detects a few date formats as well. Any column already converted by Excel or Jet was not included in this study.

@@

\subsubsection{Sampling}
The remaining samples were hashed and sorted on the hash value, with the top $32$ values being retained as the column's sample. We can increase the sample size if needed, but for dates, it appears to be an adequate number. In any case, the median number of non-null rows per domain in our test data is $50$, so increasing the sample size would have little benefit.

@@

\subsubsection{Natural Language Processing}

We implemented the grammar, training and parsing in Python 3.4.1 using the Natural Language Toolkit libraries~\cite{nltk} on a quad core Dell T7600 running Windows 7. The complexity of the CYK parsing algorithm is $O(n^{3}|G|)$, where $n$ is the length of the input and $|G|$ is the size of the grammar~\cite{Younger67}. The PCFG grammar uses a set of $22$ phrase-level non-terminals and $30$ terminals to classify the various constituents in the corpus. Because the CYK algorithm finds the maximum likelihood solution, there are no search errors (rather probability $p = 0$, and a modification in the grammar is required to improve accuracy.
